Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}

### 2017-08-01 ident_manu.Rnw
new model fig

\author{John C. Lehrter}
\address{Dauphin Island Sea Lab, University of South Alabama, Dauphin Island, AL 36528}
\ead{jlehrter@disl.org}

@@

Hypoxic events, defined  as $<$2 mg L$^{-1}$ of \ac{do} ($<$ 64 mmol m$^{-3}$), occur seasonally in bottom waters in the northern \ac{gom}.  The hypoxic area averages 15,540 km$^2$ annually (1993-2015) with minimum concentrations observed from late spring to early fall.  Seasonal variation is strongly related to carbon and nutrient export from the \ac{marb} \citep{Lohrenz08,Bianchi10}, whereas hydrologic variation, currents, and wind patterns can affect vertical salinity gradients that contribute to hypoxia formation \citep{Wiseman97,Paerl98,Obenour15}. The \ac{cgem} was developed to describe hypoxia dynamics on the \ac{lcs} and includes elements from the Navy Coastal Ocean Model \citep{Martin00} for hydrodynamics and a biogeochemical model with multiple plankton groups, water-column metabolism, and sediment diagenesis \citep[\cref{fig:mod_schem},][]{Eldridge10}.  The hydrodynamic component of \ac{cgem} provides a spatially-explicit description of hypoxia using an orthogonal grid with an approximate horizontal resolution of 1.9 km$^2$ and twenty equally-spaced vertical sigma layers on the shelf.  The biogeochemical component includes equations for 36 state variables including six phytoplankton groups (with nitrogen and phosophorus quotas for each), two zooplankton groups, nitrate, ammonium, phosphate, dissolved inorganic carbon, oxygen, silica, and multiple variables for dissolved and particulate organic matter from different sources.

@@

% model schematic
\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{figs/mod_schem.pdf}
\caption{Conceptual representation of biogeochemical components modelled in \ac{cgem} (complete equations in \citealt{Eldridge10}). FishTank implements a \ac{zerod} version of the model that does not include any advection, mixing, or sediment diagenesis.}
\label{fig:mod_schem}
\end{figure}

>>>>

\author{John C. Lehrter}
\address{University of South Alabama, Dauphin Island Sea Lab, Dauphin Island, AL 36528}
\ead{jlehrter@disl.org}

@@

Hypoxic events, defined  as $<$2 mg L$^{-1}$ of \ac{do} ($<$ 64 mmol m$^{-3}$), occur seasonally in bottom waters in the northern \ac{gom}.  The hypoxic area averages 15,540 km$^2$ annually (1993-2015) with minimum concentrations observed from late spring to early fall.  Seasonal variation is strongly related to carbon and nutrient export from the \ac{marb} \citep{Lohrenz08,Bianchi10}, whereas hydrologic variation, currents, and wind patterns can affect vertical salinity gradients that contribute to hypoxia formation \citep{Wiseman97,Paerl98,Obenour15}. The \ac{cgem} was developed to describe hypoxia dynamics on the \ac{lcs} and includes elements from the Navy Coastal Ocean Model \citep{Martin00} for hydrodynamics and a biogeochemical model with multiple plankton groups, water-column metabolism, and sediment diagenesis \citep[\cref{fig:fishmod},][]{Eldridge10}.  The hydrodynamic component of \ac{cgem} provides a spatially-explicit description of hypoxia using an orthogonal grid with an approximate horizontal resolution of 1.9 km$^2$ and twenty equally-spaced vertical sigma layers on the shelf.  The biogeochemical component includes equations for 36 state variables including six phytoplankton groups (with nitrogen and phosophorus quotas for each), two zooplankton groups, nitrate, ammonium, phosphate, dissolved inorganic carbon, oxygen, silica, and multiple variables for dissolved and particulate organic matter from different sources.

@@

% model schematic
\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{figs/fishmod.pdf}
\caption{Conceptual representation of biogeochemical components included in FishTank (complete equations in \citealt{Eldridge10}). The \acl{cgem} couples FishTank with a hydrodynamic model that includes advection, mixing, and dispersion.}
\label{fig:mod_schem}
\end{figure}

### 2017-08-01 ident_manu.tex
new model fig

\title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
\tnotetext[mytitlenote]{Version: Mon Jul 31 17:43:04 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/03ef21c36dd48fe1a6afd2f825a9bd6aaa19f078}{03ef21c36dd48fe1a6afd2f825a9bd6aaa19f078}\newline Acronyms: \acfi{chla}; \acfi{cgem}; \acfi{do}; \acfi{dom}; \acfi{gom}; \acfi{lcs}; \acfi{marb}; \acfi{pom}; \acfi{rmse}; \acfi{zerod}}

>>>>

\title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
\tnotetext[mytitlenote]{Version: Tue Aug 1 13:06:48 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/8169e808436dd5e6f70a58cb58addf7a41d98b7b}{8169e808436dd5e6f70a58cb58addf7a41d98b7b}\newline Acronyms: \acfi{chla}; \acfi{cgem}; \acfi{do}; \acfi{dom}; \acfi{gom}; \acfi{lcs}; \acfi{marb}; \acfi{pom}; \acfi{rmse}; \acfi{zerod}}
